---
title: "ILO - Project Markdown"
author: "Milo Skovfoged"
date: "27/4/2021"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
#library(readbulk)
library(lubridate)
library(fs)
library(R.utils)
#library(zoo)
library(Rilostat)
library(plotly)
library(hrbrthemes)
library(GGally)
library(viridis)
```

# Analysis of Fatalities

## Import, clean, and merged data 

First we download the Fatility data. We download the normalized data per 100.000 worker (SDG_F881_SEX_MIG_RT_A)

```{r DownloadFatility, echo=FALSE}
Fatilities <- get_ilostat(id = 'SDG_F881_SEX_MIG_RT_A', 
                          segment = 'indicator', 
                          time_format = "num",
                          filters = list(sex ="SEX_T",
                                         classif1 = "MIG_STATUS_TOTAL"), 
                          cache = FALSE) %>% 
  filter(str_sub(ref_area,1,1) != 'X') %>%
  select(ref_area, obs_value, time, classif1) %>%
  left_join(Rilostat:::ilostat_ref_area_mapping %>%
              select(ref_area) %>%
              label_ilostat(code = 'ref_area'),
            by = "ref_area") %>%
  rename(TotalFatilitiesNormP100K = obs_value)

summary(Fatilities)

Fatilities %>%
  filter(TotalFatilitiesNormP100K < 25) %>%
  ggplot(aes(x=TotalFatilitiesNormP100K)) + 
  geom_density() +  
  #geom_vline(aes(xintercept=median(TotalFatilitiesNormP100K)),
  #          color="blue", linetype="dashed", size=1) +
  theme_bw()
```

Then we download the labor inspection data. Here we download the different datasets:

1. Number of labor inspectors per 10.000 worker (LAI_INDE_NOC_RT_A)


```{r DownloadLaborInspector, echo=FALSE}
LaborInspectors <- get_ilostat(id = 'LAI_INDE_NOC_RT_A', 
                              segment = 'indicator', 
                              time_format = "num",
                              #filters = list(sex = "SEX_T"), 
                              cache = FALSE) %>% 
  filter(str_sub(ref_area,1,1) != 'X') %>%
  select(ref_area, obs_value, time) %>%
  left_join(Rilostat:::ilostat_ref_area_mapping %>%
              select(ref_area) %>%
              label_ilostat(code = 'ref_area'),
            by = "ref_area") %>%
  rename(LaborInspectorsNormP10K = obs_value)

summary(LaborInspectors)

LaborInspectors %>% ggplot(aes(x=LaborInspectorsNormP10K)) + 
  geom_density() +  
  #geom_vline(aes(xintercept=median(LaborInspectorsNormP10K)),
  #          color="blue", linetype="dashed", size=1)+
  theme_bw()
```

2. Number of inspections per inspector (LAI_VDIN_NOC_RT_A)

```{r DownloadInspectionsPerInspector, echo=FALSE}

InspectionsPerInspector <- get_ilostat(id = 'LAI_VDIN_NOC_RT_A', 
                                segment = 'indicator', 
                                time_format = "num",
                                #filters = list(sex = "SEX_T"), 
                                cache = FALSE) %>% 
  filter(str_sub(ref_area,1,1) != 'X') %>%
  select(ref_area, obs_value, time) %>%
  left_join(Rilostat:::ilostat_ref_area_mapping %>%
              select(ref_area) %>%
              label_ilostat(code = 'ref_area'),
            by = "ref_area") %>%
  rename(InspectionsPerInspector = obs_value)

summary(InspectionsPerInspector)

InspectionsPerInspector %>% ggplot(aes(x=InspectionsPerInspector)) + 
  geom_density()+  
  #geom_vline(aes(xintercept=median(InspectionsPerInspector)),
  #          color="blue", linetype="dashed", size=1)+
  theme_bw()
```

3. Total number of inspections (LAI_VIST_NOC_NB_A)

```{r DownloadNumLaborInspections, echo=FALSE}

NubLaborInspections <- get_ilostat(id = 'LAI_VIST_NOC_NB_A', 
                               segment = 'indicator', 
                               time_format = "num",
                               #filters = list(sex = "SEX_T"), 
                               cache = FALSE) %>% 
  filter(str_sub(ref_area,1,1) != 'X') %>%
  select(ref_area, obs_value, time) %>%
  left_join(Rilostat:::ilostat_ref_area_mapping %>%
              select(ref_area) %>%
              label_ilostat(code = 'ref_area'),
            by = "ref_area") %>%
  rename(TotalLaborInspections = obs_value)

summary(NubLaborInspections)

NubLaborInspections %>% ggplot(aes(x=TotalLaborInspections)) + 
  geom_density()+  
  #geom_vline(aes(xintercept=median(TotalLaborInspections)),
  #          color="blue", linetype="dashed", size=1)+
  theme_bw()

```

Them we combine and clean the data.

```{r CleanAndMergeFatalities, echo=FALSE}
CombinedFatilityData <- Fatilities %>%
  dplyr::full_join(LaborInspectors, by = c("ref_area", "time", "ref_area.label"), copy = FALSE, keep = FALSE) %>%
  dplyr::full_join(NubLaborInspections, by = c("ref_area", "time", "ref_area.label"), copy = FALSE, keep = FALSE) %>%
  dplyr::full_join(InspectionsPerInspector, by = c("ref_area", "time", "ref_area.label"), copy = FALSE, keep = FALSE)

col_order <- c("ref_area", "ref_area.label", "classif1", "time", "TotalFatilitiesNormP100K", "LaborInspectorsNormP10K", "InspectionsPerInspector", "TotalLaborInspections")

CombinedFatilityData <- CombinedFatilityData[, col_order]

CombinedFatilityDataNoNA <- CombinedFatilityData %>% drop_na()

skimmedDownCombinedFatilityDataNoNA <- CombinedFatilityDataNoNA[CombinedFatilityDataNoNA$ref_area %in% names(which(table(CombinedFatilityDataNoNA$ref_area) > 4)), ]

summary(skimmedDownCombinedFatilityDataNoNA)
```

An initial linear regission analysis explains Fatilities very little (R-squared:  0.04)

It indicates a very small statical significants. The number of inspections per inspector increases the number of Fatilities

However, the 
 
```{r SummeryOfFatilityData, echo = FALSE}
summary(lm(TotalFatilitiesNormP100K ~ LaborInspectorsNormP10K * InspectionsPerInspector, data = skimmedDownCombinedFatilityDataNoNA))
```

```{r PlotFatalies, echo=FALSE}
# Labor Inspectors
skimmedDownCombinedFatilityDataNoNA %>% ggplot(aes(x = TotalFatilitiesNormP100K, 
               y = LaborInspectorsNormP10K,
               color = time
               ),
               alpha(0.5),
) + 
  geom_point() +
  geom_smooth(method=lm,
              se = F) +
  theme_bw()

skimmedDownCombinedFatilityDataNoNA %>% ggplot(aes(x = TotalFatilitiesNormP100K, 
               y = LaborInspectorsNormP10K,
               color = time),
               alpha(0.5),
) + 
  geom_point() +
  geom_smooth(method=lm,
              se = F) +
  facet_wrap(~ref_area.label) +
  theme_bw()

skimmedDownCombinedFatilityDataNoNA %>% ggplot(aes(x = TotalFatilitiesNormP100K, 
               y = InspectionsPerInspector,
               color = time
               ),
               alpha(0.5),
) + 
  geom_point() +
  geom_smooth(method=lm,
              se = F) +
  theme_bw()

skimmedDownCombinedFatilityDataNoNA %>% 
  ggplot(aes(x = TotalFatilitiesNormP100K, 
               y = InspectionsPerInspector,
               color = time,
               alpha = 0.5)
) + 
  geom_point() +
  geom_smooth(method=lm,
              se = F) +
  facet_wrap(~ref_area.label) +
  theme_bw()
```

# Analysis of injuries

```{r DownloadInjury, echo=FALSE}
Injuries <- get_ilostat(id = 'SDG_N881_SEX_MIG_RT_A', 
                          segment = 'indicator', 
                          time_format = "num",
                          filters = list(sex ="SEX_T",
                                         classif1 = "MIG_STATUS_TOTAL"
                                         #year = c(2010,2011,2012,2013,2014,2015,2016,2017,2018,2019)
                                         ), 
                          cache = FALSE) %>% 
  filter(str_sub(ref_area,1,1) != 'X') %>%
  select(ref_area, obs_value, time, classif1) %>%
  left_join(Rilostat:::ilostat_ref_area_mapping %>%
              select(ref_area) %>%
              label_ilostat(code = 'ref_area'),
            by = "ref_area") %>%
  rename(TotalInjuriesNormP100K = obs_value)

summary(Injuries)

Injuries %>%
  filter(TotalInjuriesNormP100K < 2000) %>%
  ggplot(aes(x=TotalInjuriesNormP100K)) + 
  geom_density() +  
  #geom_vline(aes(xintercept=median(TotalFatilitiesNormP100K)),
  #          color="blue", linetype="dashed", size=1) +
  theme_bw()
```


Them we combine and clean the injury data.

```{r CleanAndMergeInjury, echo=FALSE}
CombinedInjuryData <- Injuries %>%
  dplyr::full_join(LaborInspectors, by = c("ref_area", "time", "ref_area.label"), copy = FALSE, keep = FALSE) %>%
  dplyr::full_join(NubLaborInspections, by = c("ref_area", "time", "ref_area.label"), copy = FALSE, keep = FALSE) %>%
  dplyr::full_join(InspectionsPerInspector, by = c("ref_area", "time", "ref_area.label"), copy = FALSE, keep = FALSE)

col_order <- c("ref_area", "ref_area.label", "classif1", "time", "TotalInjuriesNormP100K", "LaborInspectorsNormP10K", "InspectionsPerInspector", "TotalLaborInspections")

CombinedInjuryData <- CombinedInjuryData[, col_order]

CombinedInjuryDataNoNA <- CombinedInjuryData %>% drop_na()
```


```{r SummeryOfInjuryData, echo = FALSE}
summary(lm(TotalInjuriesNormP100K ~ LaborInspectorsNormP10K * InspectionsPerInspector, data = CombinedInjuryDataNoNA))
```

```{r PlotInjuries, echo=FALSE}
# Labor Inspectors
CombinedInjuryDataNoNA %>% ggplot(aes(x = TotalInjuriesNormP100K, 
               y = LaborInspectorsNormP10K,
               color = time
               ),
               alpha(0.5),
) + 
  geom_point() +
  geom_smooth(method=lm,
              se = F) +
  theme_bw()

CombinedInjuryDataNoNA %>% 
  filter(LaborInspectorsNormP10K < 25) %>%
  ggplot(aes(y = TotalInjuriesNormP100K, 
               x = LaborInspectorsNormP10K,
               color = time),
               alpha(0.5),
) + 
  geom_point() +
  geom_smooth(method=lm,
              se = F) +
  facet_wrap(~ref_area.label) +
  theme_bw()

CombinedInjuryDataNoNA %>% ggplot(aes(x = TotalInjuriesNormP100K, 
               y = InspectionsPerInspector,
               color = time
               ),
               alpha(0.5),
) + 
  geom_point() +
  geom_smooth(method=lm,
              se = F) +
  theme_bw()

CombinedInjuryDataNoNA %>% ggplot(aes(y = TotalInjuriesNormP100K, 
               x = InspectionsPerInspector,
               color = time,
               alpha = 0.5)
) + 
  geom_point() +
  geom_smooth(method=lm,
              se = F) +
  facet_wrap(~ref_area.label) +
  theme_bw()
```

# Parallel Coordinates Chart

```{r ParallelCoordinatesChart, echo=FALSE}

skimmedDownCombinedFatilityDataNoNA %>% 
  ggplot(aes(x = TotalFatilitiesNormP100K, 
               y = InspectionsPerInspector,
               color = time,
               alpha = 0.5)
) + 
  geom_point() +
  geom_smooth(method=lm,
              se = F) +
  facet_wrap(~ref_area.label) +
  theme_bw()

ggparcoord(skimmedDownCombinedFatilityDataNoNA,
    columns = 5:7, groupColumn = 2,
    showPoints = TRUE, 
    alphaLines = 0.3
    )+
  theme_ipsum()


skimmedDownCombinedDataNoNA <- skimmedDownCombinedFatilityDataNoNA %>%
  dplyr::full_join(Injuries, by = c("ref_area", "time", "ref_area.label", "classif1"), copy = FALSE, keep = FALSE) %>% drop_na()

skimmedDownCombinedDataNoNA <- skimmedDownCombinedDataNoNA %>% 
  mutate(InspectorsTimesInspactions = LaborInspectorsNormP10K * InspectionsPerInspector)

col_order <- c("ref_area", "ref_area.label", "classif1", "time", "TotalFatilitiesNormP100K", "TotalInjuriesNormP100K", "LaborInspectorsNormP10K", "InspectionsPerInspector", "InspectorsTimesInspactions", "TotalLaborInspections")

skimmedDownCombinedDataNoNA <- skimmedDownCombinedDataNoNA[, col_order]

ggparcoord(skimmedDownCombinedDataNoNA,
    columns = 5:9, groupColumn = 2,
    scale="center",
    showPoints = TRUE, 
    alphaLines = 0.3
    )+
  theme_ipsum()

skimmedDownCombinedDataNoNAMean <- skimmedDownCombinedDataNoNA %>%
  group_by(ref_area.label) %>%
  dplyr::summarize(mTotalFatilitiesNormP100K = mean(TotalFatilitiesNormP100K),
         meanTotalInjuriesNormP100K = mean(TotalInjuriesNormP100K),
         meanLaborInspectorsNormP10K = mean(LaborInspectorsNormP10K),
         meanInspectionsPerInspector = mean(InspectionsPerInspector),
         meanInspectorsTimesInspactions = mean(InspectorsTimesInspactions))
  
ggparcoord(skimmedDownCombinedDataNoNAMean,
    columns = 2:6, groupColumn = 1,
    scale="center",
    showPoints = TRUE, 
    alphaLines = 0.3
    )+
  theme_ipsum()



skimmedDownCombinedDataNoNA %>% 
  # group by city
  group_by(ref_area.label) %>%
  # initiate a plotly object with date on x and median on y
  plot_ly(x = ~time, y = ~TotalFatilitiesNormP100K) %>%
  # add a line plot for all texan cities
  add_lines( hoverinfo = "none", 
            type = "scatter", mode = "lines", 
            line = list(color = 'rgba(192,192,192,0.4)'))
```